---
title: "Review of Data"
subtitle: "London East Asia Film Festival (LEAFF) 2017"
author: "[Avision Ho](https://github.com/avisionh)"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include = FALSE}
# For markdown template
library(tufte)

# Load relevant packages for project
vec_packages <- c("readxl", "janitor", "magrittr", "dplyr", "tidyr", "tibble", "ggplot2", "scales", "knitr")
pacman::p_load(char = vec_packages, install = TRUE)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(results = "asis", warning = FALSE, message = FALSE)

# Load scripts
source("scripts/0 - functions.R")
source("scripts/1.1 - dataImportClean.R")
source("scripts/1.2 - dataWrangle.R")

# Turn off scientific notation
options(scipen = 999, expressions = 10000)

cb_palette <- c("cb_black" = "#000000",
                "cb_grey" = "#999999",
                "cb_orange" = "#E69F00",
                "cb_light_blue" = "#56B4E9",
                "cb_green" = "#009E73",
                "cb_yellow" = "#F0E442",
                "cb_dark_blue" = "#0072B2",
                "cb_red" = "#D55E00",
                "cb_pink" = "#CC79A7")

rm(vec_packages)
```

# Executive Summary

***

# Introduction
`r newthought('This paper analyses the data')` collected from the London East Asia Film Festival (LEAFF) 2017. It does so with the intention of providing a summary of how the successful the event was, and to provide a benchmark for future editions of LEAFF.

***

# Section 1: General Information
`r newthought("This section presents")` a general high-level overview of the film shown and where they were screened.

```{r (HIDE) 1, include = FALSE, echo = FALSE}
# Create text for film titles
txt_film_titles <- data_activity_fund %>% 
  head(5) %>% 
  select(FilmTitle, YearOfRelease) %>% 
  mutate(DummyText_1 = " (", DummyText_2 = ")") %>% 
  select(FilmTitle, DummyText_1, YearOfRelease, DummyText_2) %>% 
  unite(col = Text, FilmTitle, DummyText_1, YearOfRelease, DummyText_2, sep = "") %>% 
  pull()
txt_film_titles <- paste0(txt_film_titles[1:4]) %>% 
  append(txt_film_titles[5])

# Create text for film screenings
txt_film_screenings <- data_activity_fund %>% 
  distinct(VenueName) %>% 
  pull()
txt_film_screenings <- paste0(txt_film_screenings[1:3]) %>% 
  append(txt_film_screenings[8])

# Create text for accessibility
n <- nrow(data_activity_fund)

n_access <- data_activity_fund %>% 
  filter(was_this_an_accessibility_screening == "Yes") %>% 
  nrow()
  
n_subtitles <- data_activity_fund %>% 
  filter(if_this_was_accessible_you_can_show_us_which_type_using_dropdown_the_options == "Captioned / Descriptive Subtitles") %>% 
  nrow()
  
if (n == n_access) {
  txt_access <- "all"
} else if(n/2 < n_access) {
  txt_access <- "most"
} else if (n_access > 0) {
  txt_access <- "some"
} else {
  txt_access <- "none"
}

if (n_access == n_subtitles) {
  txt_subtitles <- "all"
} else if(n_access/2 < n_subtitles) {
  txt_subtitles <- "most"
} else if (n_subtitles > 0) {
  txt_subtitles <- "some"
} else {
  txt_subtitles <- "none"
}

# Create text for events
txt_event <- data_activity_fund %>% 
  filter(!is.na(event_type_where_more_than_just_a_screening_eg_q_a)) %>% 
  distinct(event_type_where_more_than_just_a_screening_eg_q_a) %>% 
  pull()
txt_event <- paste0(txt_event[1:length(txt_event)-1]) %>% 
  append(txt_event[nrow(txt_event)])

```

## Section 1.1: Films Shown and Locations

+ For the 2017 festival a wide range of films from different nations that included South Korea, Japan, Hong Kong, Vietnam, and the Phillippines were shown. ^[[Full programme here](https://www.leaff.org.uk/programme-2/)] These included `r toString(txt_film_titles)`. 

+ The screenings for these films took place in a variety of locations, mostly in London, but with a few in other regions in the UK. These included `r toString(txt_film_screenings)`.

## Section 1.2: Accessibility
+ For each of these film screenings, `r toString(txt_access)` of them were an **accessibility screening**. Of those that were an **accessbility screening**, `r toString(txt_subtitles)` of them had descriptive subtitles and/or were captioned.

## Section 1.3: Additional Events
+ Beyond showing films, LEAFF 2017 offered audiences the chance to be more involved with films and cinema by hosting a series of events to accompany some of the festival's film screenings. These events involved sessions such as `r toString(txt_event)`.

## Section 1: Summary
Given the range of films screened, the way these screenings met accessibility requirements, and the additional events that were hosted during the festival to complement the films, then LEAFF 2017 offered all audiences an eclectic range of activities and films to enjoy.

***

# Section 2: Audience Demographics
`r newthought("This section presents")` data on the demographics of people who have attended LEAFF 2017, and filled in our post-screening surveys.

```{r 1. (HIDE) Remove variables, include = FALSE, echo = FALSE}
rm(txt_access, txt_event, txt_film_screenings, txt_film_titles, txt_subtitles)
```


## Section 2.1: Gender
```{r (HIDE) 2.1 Gender - text, include = FALSE, echo = FALSE}
data_gender <- data_demographics %>% 
  filter(Category == "Gender" & Field != "prefer not to say / did not answer") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2))

value_female <- data_gender %>% 
  filter(Field == "Female") %>% 
  select(Percent) %>% 
  pull()
value_male <- data_gender %>% 
  filter(Field == "Male") %>% 
  select(Percent) %>% 
  pull()

# Create text for gender closeness
if(value_female == value_male) {
  txt_gender <- "equal"
} else if (abs(value_female - value_male) < 0.3) {
  txt_gender <- "similar"
} else {
  txt_gender <- "far apart"
}
```

```{r (SHOW) 2.1 Gender - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 1", fig.width = 5, fig.height = 3}
func_plot_pie(x = data_gender, col_counts = "Percent", col_category = "Field", 
              plot_title = "Gender", factor_levels = c("Male", "Female"))
```
+ In **Figure 1**, the female-to-male proportion of audience who went to the film screenings during the festival and completed this field in the post-film survey  is `r toString(txt_gender)`, `r toString(paste0(value_female * 100, "%"))` to `r toString(paste0(value_male * 100, "%"))`.

## Section 2.2: Age
```{r (HIDE) 2.2 Age - text, include = FALSE, echo = FALSE}
data_age <- data_demographics %>% 
  filter(Category == "Age") %>% 
  arrange(desc(Value))

txt_age <- data_age %>% 
  select(Field) %>% 
  head(3) %>% 
  pull()
```
```{r (SHOW) 2.2 Age - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 2", fig.width = 5, fig.height = 3}
func_plot_counts_percents(x = filter(.data = data_demographics_master, Category == "Age"), col_x = "Field",
                          colour_fill = cb_palette[["cb_orange"]], plot_title = "Age", plot_title_x = "Age")
```
+ In **Figure 2**, the largest three age groups for our audience who went to the film screenings during the festival and completed this field in the post-film survey are the `r toString(txt_age)` categories. 

+ This ties in with the festival's aim to attract and engage young age groups in film and cinema, as it is the young age groups who will be the future consumers of film and cinema.


## Section 2.3: Ethnicity
```{r (HIDE) 2.3 Ethnicity - text, include = FALSE, echo = FALSE}
data_ethnicity <- data_demographics %>% 
  filter(Category == "Ethnicity") %>% 
  arrange(desc(Value)) %>% 
  select(Field, Value)

txt_ethnicity <- data_ethnicity %>% 
  head(3) %>% 
  select(Field) %>% 
  pull()
txt_ethnicity_top_two <- data_ethnicity %>% 
  mutate(OpenBracket = " (", EndBracket = ")") %>%
  select(Field, OpenBracket, Value, EndBracket) %>% 
  head(2) %>% 
  unite(col = Text, Field, OpenBracket, Value, EndBracket, sep = "")
```
```{r (SHOW) 2.3 Ethnicity - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 3", fig.width = 5, fig.height = 3}
func_plot_counts_percents(x = filter(.data = data_demographics_master, Category == "Ethnicity"), col_x = "Field",
                          colour_fill = cb_palette[["cb_light_blue"]], plot_title = "Ethnicity", plot_title_x = "Ethnicity")
```
+ In **Figure 3**, the largest three ethnicity groups for our audience who went to the film screenings during the festival and completed this field in the post-film survey are `r toString(txt_ethnicity)`.

```{marginfigure}
_This would appeal most to sponsors who want to improve their brand exposure to different ethnic groups._
```

+ Notice in particular that the number of *`r toString(txt_ethnicity_top_two[1,])`* and *`r toString(txt_ethnicity_top_two[2,])`* ethnic groups who attended LEAFF 2017 are very close. This demonstrates that the film festival is effetive in appealing to both an East Asian and non-East Asian audiences.

## Section 2: Summary
Given the relatively equal split between genders, the popularity of the festival with younger age groups, and the festival's ability to attract both East Asian and non-East Asian ethnic groups, LEAFF 2017 was effective in catering to the key audience group of younger adults equally between genders, and within this subgroup, attracting a wide range of people from different ehtnic backgrounds.

***

# Section 3: Key Performance Metrics
`r newthought("This section presents")` key analyis of the festival's performance data.
```{r 2. (HIDE) Remove variables, include = FALSE, echo = FALSE}
rm(data_gender, data_age, data_ethnicity, txt_gender, value_male, value_female,
   txt_age, txt_ethnicity, txt_ethnicity_top_two)
```

## Section 3.1: Total admissions for each film
```{r (HIDE) 3.1 Admissions - text, echo = FALSE, include = FALSE}
data_admissions <- data_activity_fund %>% 
  filter(!(YearOfRelease %in% c("various", "__"))) %>% 
  select(FilmTitle:YearOfRelease, TotalAdmissions) %>%
  # get proper ordering of most popular films
  group_by(FilmTitle) %>% 
  summarise(TotalAdmissionsOverall = sum(TotalAdmissions)) %>% 
  arrange(desc(TotalAdmissionsOverall)) %>% 
  left_join(y = data_activity_fund, by = "FilmTitle") %>% 
  select(FilmTitle, YearOfRelease, VenueName, TotalAdmissionsOverall, TotalAdmissions) %>% 
  rename(TotalAdmissionsByCinema = TotalAdmissions)

# Create table for printing
table_admissions <- data_admissions %>% 
  distinct(FilmTitle, .keep_all = TRUE) %>% 
  select(-TotalAdmissionsByCinema) %>% 
  rename(Film = FilmTitle,
         `Release Year` = YearOfRelease,
         Venue = VenueName,
         `Total Admissions` = TotalAdmissionsOverall) %>% 
  head(5) 

n_open_gala <- 1679
n_admissions_gala <- table_admissions %>% 
  head(1) %>% 
  select(`Total Admissions`) %>% 
  pull()
value_gala_admissions_proportion <- (n_admissions_gala / n_open_gala) * 100
value_gala_admissions_proportion <- round(x = value_gala_admissions_proportion, digits = 2)
```
```{r (SHOW) 3.1 Admissions - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 4", fig.width = 7, fig.height = 10}
ggplot(data = data_admissions, 
       mapping = aes(x = reorder(x = FilmTitle, X = TotalAdmissionsOverall), y = TotalAdmissionsByCinema)) +
  geom_bar(mapping = aes(fill = factor(VenueName)), stat = "identity") +
  coord_flip() +
  labs(title = "Bar Chart: Total Admissions by Film and Venue", subtitle = "LEAFF 2017", 
       x = "Film", y = "Total Admissions", fill = "Venue") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
                      plot.subtitle = element_text(face = "bold", hjust = 0.5),
                      panel.background = element_blank(),
                      axis.line = element_line(color = cb_palette["cb_black"]))
```
+ In **Figure 4**, we have the number of people who bought tickets for each of the film screenings, with the colour-coding distinguishing which films were shown in which cinemas. In particular, it is worth noting that the most-watched film, *The Fortress*, was held at *Odeon Leicester Square*, which has a screen capacity of *`r toString(n_open_gala)`*; whereas the other cinemas where films were shown have much smaller capacities. 

+ The table below focusses on the key insight of the most popular films that can be drawn from **Figure 4**. Whilst we do not possess data on the seating capacity for each venue, and consequently cannot make a more accurate inference on which films sold the most tickets relative to the number of tickets available, we do know that for opening gala film, *The Fortress*, `r toString(paste0(value_gala_admissions_proportion, "%"))` of available tickets were sold.
```{r (SHOW) 3.1 Admissions - table, echo = FALSE}
kable(table_admissions, caption = "_The most popular films by admissions for LEAFF 2017_")
```

## Section 3.2: Retaining old audiences and capturing new audiences
```{r (HIDE) 3.2 Retention - text, echo = FALSE, include = FALSE}
data_retention <- data_demographics %>% 
  filter(Category == "New   Audience" & Field != "Prefer not to say / did not answer") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2)) %>% 
  arrange(desc(Value))

txt_retention_first <- data_retention %>% 
  head(1)
txt_retention_first <- paste0(select(.data = txt_retention_first, Value),
                              " of LEAFF 2017 attendees saying ", 
                              "\"", select(.data = txt_retention_first, Field), "\"")
txt_retention_second <- data_retention[2, ]
txt_retention_second <- paste0(select(.data = txt_retention_second, Value),
                              " of LEAFF 2017 attendees saying ", 
                              "\"", select(.data = txt_retention_second, Field), "\"")
```
```{r (SHOW) 3.2 Retention - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 5", fig.width = 6, fig.height = 5}
lvls <- c("Been to LEAFF 2015", "Been to LEAFF 2016",
          "Been to both", "This is my first time")
func_plot_pie(x = data_retention, col_counts = "Percent", col_category = "Field", 
              plot_title = "Audience Retention", factor_levels = lvls)
```
+ In **Figure 5**, we have `r toString(txt_retention_first)` and `r toString(txt_retention_second)`. 

+ These were the top two responses and demonstrates that LEAFF 2017's marketing strategy was effective in encouraging attendees from 2016 to return to LEAFF 2017 and in attracting new attendees.

## Section 3.3: Audience rating of their LEAFF 2017 experience
```{r (HIDE) 3.3 Rating- text, echo = FALSE, include = FALSE}
data_rating <- data_demographics %>% 
  filter(Category == "Rating of the experience") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2)) 

txt_rating <- data_rating %>% 
  filter(Field %in% c("Brilliant       *****", "****"))
txt_rating <- sum(x = txt_rating$Percent)

if (txt_rating > 0.7) {
  txt_rating_conc <- c("the majority of", "successful")
} else if (txt_rating > 0.5) {
  txt_rating_con <- c("over half of", "successful")
} else {
  txt_rating_conc <- c("some", "unsuccessful")
}
```
```{r (SHOW) 3.3 Rating - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 6", fig.width = 5, fig.height = 4}
lvls <- c("Brilliant       *****", "****", "***", "**", "Poor *")
data_rating <- data_demographics_master %>% 
  filter(Category == "Rating of the experience") %>% 
  mutate(Field = factor(x = Field, levels = lvls))
func_plot_counts_percents(x = data_rating, 
                          col_x = "Field",
                          colour_fill = cb_palette[["cb_green"]], 
                          plot_title = "Rating of Experience", 
                          plot_title_x = "Rating")
```
+ In **Figure 6**, `r toString(paste0(txt_rating * 100, "%"))` of attendees rated their LEAFF 2017 experience as being either **Brilliant \*\*\*\*\* ** (*five stars*) or **Good \*\*\*\* ** (*four stars*).

+ This demonstrates that `r toString(txt_rating_conc[1])` attendees enjoyed LEAFF 2017 and that the programme and activities which were part of this were `r toString(txt_rating_conc[2])` in capturing the public's interests and appetite for film and cinema.

## Section 3.4: Audience main motivation for attending

## Section 3.5: Audience likelihood of attending future LEAFFs

## Section 3: Summary

***

# Concluding Remarks

## Full Width Figures

You can arrange for figures to span across the entire page by using the chunk option `fig.fullwidth = TRUE`.

```{r fig-fullwidth, fig.width = 10, fig.height = 2, fig.fullwidth = TRUE, fig.cap = "A full width figure.", warning=FALSE, message=FALSE, cache=TRUE}
ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```

 Other chunk options related to figures can still be used, such as `fig.width`, `fig.cap`, `out.width`, and so on. For full width figures, usually `fig.width` is large and `fig.height` is small. In the above example, the plot size is $10 \times 2$.

## Main Column Figures

Besides margin and full width figures, you can of course also include figures constrained to the main column. This is the default type of figures in the LaTeX/HTML output.

```{r fig-main, fig.cap = "A figure in the main column.", cache=TRUE}
ggplot(diamonds, aes(cut, price)) + geom_boxplot()
```

# Sidenotes

One of the most prominent and distinctive features of this style is the extensive use of sidenotes. There is a wide margin to provide ample room for sidenotes and small figures. Any use of a footnote will automatically be converted to a sidenote. ^[This is a sidenote that was entered using a footnote.] 

If you'd like to place ancillary information in the margin without the sidenote mark (the superscript number), you can use the `margin_note()` function from **tufte** in an inline R expression. `r margin_note("This is a margin note.  Notice that there is no number preceding the note.")` This function does not process the text with Pandoc, so Markdown syntax will not work here. If you need to write anything in Markdown syntax, please use the `marginfigure` block described previously.

# References

References can be displayed as margin notes for HTML output. For example, we can cite R here [@R-base]. To enable this feature, you must set `link-citations: yes` in the YAML metadata, and the version of `pandoc-citeproc` should be at least 0.7.2. You can always install your own version of Pandoc from http://pandoc.org/installing.html if the version is not sufficient. To check the version of `pandoc-citeproc` in your system, you may run this in R:

```{r eval=FALSE}
system2('pandoc-citeproc', '--version')
```

If your version of `pandoc-citeproc` is too low, or you did not set `link-citations: yes` in YAML, references in the HTML output will be placed at the end of the output document.

# Tables

You can use the `kable()` function from the **knitr** package to format tables that integrate well with the rest of the Tufte handout style. The table captions are placed in the margin like figures in the HTML output.

```{r}
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)
```

# Block Quotes

We know from the Markdown syntax that paragraphs that start with `>` are converted to block quotes. If you want to add a right-aligned footer for the quote, you may use the function `quote_footer()` from **tufte** in an inline R expression. Here is an example:

> "If it weren't for my lawyer, I'd still be in prison. It went a lot faster with two people digging."
>
> `r tufte::quote_footer('--- Joe Martin')`

Without using `quote_footer()`, it looks like this (the second line is just a normal paragraph):

> "Great people talk about ideas, average people talk about things, and small people talk about wine."
>
> --- Fran Lebowitz

# Responsiveness

The HTML page is responsive in the sense that when the page width is smaller than 760px, sidenotes and margin notes will be hidden by default. For sidenotes, you can click their numbers (the superscripts) to toggle their visibility. For margin notes, you may click the circled plus signs to toggle visibility.

# More Examples

The rest of this document consists of a few test cases to make sure everything still works well in slightly more complicated scenarios. First we generate two plots in one figure environment with the chunk option `fig.show = 'hold'`:

```{r fig-two-together, fig.cap="Two plots in one figure environment.", fig.show='hold', cache=TRUE, message=FALSE}
p <- ggplot(mtcars2, aes(hp, mpg, color = am)) +
  geom_point()
p
p + geom_smooth()
```

Then two plots in separate figure environments (the code is identical to the previous code chunk, but the chunk option is the default `fig.show = 'asis'` now):

```{r fig-two-separate, ref.label='fig-two-together', fig.cap=sprintf("Two plots in separate figure environments (the %s plot).", c("first", "second")), cache=TRUE, message=FALSE}
```

You may have noticed that the two figures have different captions, and that is because we used a character vector of length 2 for the chunk option `fig.cap` (something like `fig.cap = c('first plot', 'second plot')`).

Next we show multiple plots in margin figures. Similarly, two plots in the same figure environment in the margin:

```{r fig-margin-together, fig.margin=TRUE, fig.show='hold', fig.cap="Two plots in one figure environment in the margin.", fig.width=3.5, fig.height=2.5, cache=TRUE}
p
p + geom_smooth(method = 'lm')
```

Then two plots from the same code chunk placed in different figure environments:

```{r fig-margin-separate, fig.margin=TRUE, fig.cap=sprintf("Two plots in separate figure environments in the margin (the %s plot).", c("first", "second")), fig.width=3.5, fig.height=2.5, cache=TRUE}
knitr::kable(head(iris, 15))
p
knitr::kable(head(iris, 12))
p + geom_smooth(method = 'lm')
knitr::kable(head(iris, 5))
```

We blended some tables in the above code chunk only as _placeholders_ to make sure there is enough vertical space among the margin figures, otherwise they will be stacked tightly together. For a practical document, you should not insert too many margin figures consecutively and make the margin crowded. 

You do not have to assign captions to figures. We show three figures with no captions below in the margin, in the main column, and in full width, respectively.

```{r fig-nocap-margin, fig.margin=TRUE, fig.width=3.5, fig.height=2, cache=TRUE}
# a boxplot of weight vs transmission; this figure
# will be placed in the margin
ggplot(mtcars2, aes(am, wt)) + geom_boxplot() +
  coord_flip()
```
```{r fig-nocap-main, cache=TRUE}
# a figure in the main column
p <- ggplot(mtcars, aes(wt, hp)) + geom_point()
p
```
```{r fig-nocap-fullwidth, fig.fullwidth=TRUE, fig.width=10, fig.height=3, cache=TRUE}
# a fullwidth figure
p + geom_smooth(method = 'lm') + facet_grid(~ gear)
```

# Some Notes on Tufte CSS

There are a few other things in Tufte CSS that we have not mentioned so far. If you prefer `r sans_serif('sans-serif fonts')`, use the function `sans_serif()` in **tufte**. For epigraphs, you may use a pair of underscores to make the paragraph italic in a block quote, e.g.

> _I can win an argument on any topic, against any opponent. People know this, and steer clear of me at parties. Often, as a sign of their great respect, they don't even invite me._
>
> `r quote_footer('--- Dave Barry')`

We hope you will enjoy the simplicity of R Markdown and this R package, and we sincerely thank the authors of the Tufte-CSS and Tufte-LaTeX projects for developing the beautiful CSS and LaTeX classes. Our **tufte** package would not have been possible without their heavy lifting.

You can turn on/off some features of the Tufte style in HTML output. The default features enabled are:

```yaml
output:
  tufte::tufte_html:
    tufte_features: ["fonts", "background", "italics"]
```

If you do not want the page background to be lightyellow, you can remove `background` from `tufte_features`. You can also customize the style of the HTML page via a CSS file. For example, if you do not want the subtitle to be italic, you can define

```css
h3.subtitle em {
  font-style: normal;
}
```

in, say, a CSS file `my_style.css` (under the same directory of your Rmd document), and apply it to your HTML output via the `css` option, e.g.,

```yaml
output:
  tufte::tufte_html:
    tufte_features: ["fonts", "background"]
    css: "my_style.css"
```

There is also a variant of the Tufte style in HTML/CSS named "[Envisoned CSS](http://nogginfuel.com/envisioned-css/)". This style can be used by specifying the argument `tufte_variant = 'envisioned'` in `tufte_html()`^[The actual Envisioned CSS was not used in the **tufte** package. We only changed the fonts, background color, and text color based on the default Tufte style.], e.g.

```yaml
output:
  tufte::tufte_html:
    tufte_variant: "envisioned"
```

To see the R Markdown source of this example document, you may follow [this link to Github](https://github.com/rstudio/tufte/raw/master/inst/rmarkdown/templates/tufte_html/skeleton/skeleton.Rmd), use the wizard in RStudio IDE (`File -> New File -> R Markdown -> From Template`), or open the Rmd file in the package:

```{r eval=FALSE}
file.edit(
  tufte:::template_resources(
    'tufte_html', '..', 'skeleton', 'skeleton.Rmd'
  )
)
```

This document is also available in [Chinese](http://rstudio.github.io/tufte/cn/), and its `envisioned` style can be found [here](http://rstudio.github.io/tufte/envisioned/).

```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
