---
title: "Review of Data"
subtitle: "London East Asia Film Festival (LEAFF) 2017"
author: "[Avision Ho](https://github.com/avisionh)"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include = FALSE}
# For markdown template
library(tufte)

# Load relevant packages for project
vec_packages <- c("readxl", "janitor", "magrittr", "dplyr", "tidyr", "tibble", "ggplot2", "scales", "knitr", "pander")
pacman::p_load(char = vec_packages, install = TRUE)

# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)

knitr::opts_chunk$set(results = "asis", warning = FALSE, message = FALSE)

# Load scripts
source("scripts/0 - functions.R")
source("scripts/1.1 - dataImportClean.R")
source("scripts/1.2 - dataWrangle.R")

# Turn off scientific notation
options(scipen = 999, expressions = 10000)

cb_palette <- c("cb_black" = "#000000",
                "cb_grey" = "#999999",
                "cb_orange" = "#E69F00",
                "cb_light_blue" = "#56B4E9",
                "cb_green" = "#009E73",
                "cb_yellow" = "#F0E442",
                "cb_dark_blue" = "#0072B2",
                "cb_red" = "#D55E00",
                "cb_pink" = "#CC79A7")

rm(vec_packages)
```

# Executive Summary
```{r (HIDE) Exec Summary (also in 3.5 Future - text), echo = FALSE, include = FALSE}
table_future <- data_demographics %>% 
  filter(Category == "Likelihood of attending again?") %>% 
  mutate(Percent = Value/sum(Value)) %>% 
  select(-Category)

txt_future <- table_future %>% 
  filter(Field %in% c("Very Likely", "Likely")) %>% 
  mutate(PercentFinal = sum(x = Percent) * 100) %>% 
  distinct(PercentFinal) %>% 
  pull() %>% 
  signif(digits = 2) %>% 
  paste0("%")
```
From the data analysed in this report, the key findings are:

**The curated film programme at LEAFF 2017 catered to a mainstream and large audience, and more particularly, being of most interest to the key age groups of 20 - 30.**

**The marketing strategy attracted a good range of people from different backgrounds who were new to the festival and returned to the festival from previous years.**

**The additional events such as Q&A sessions and workshops successfully engaged audiences enough to develop their interest and intrigue in film beyond just watching film.**

**The overall delivery of the entire festival was effective in receiving positive reviews from attendees.**

**Lastly, the overall festival experience was of such quality that `r toString(txt_future)` of survey respondents will return again in the future.**

***

# Introduction

> _LEAFF aims to champion the growing collaboration in East Asian filmmaking with a philosophy that marks a shift in the cinematic landscape of East Asia, and moves away from cultural and cinematic borders. Our vision is to bring a much wider, eclectic, and diverse programme of films from over 10 countries to show the richness and diversity of the region and its people. We want to draw people in with the familiar, and offer opportunities to see something new._
>
> `r quote_footer('--- Hyejung Jeon, Festival Director')`

`r newthought('This paper analyses the data')` collected from the London East Asia Film Festival (LEAFF) 2017. It does so with the intention of providing a summary of how successful the event was, and to provide a benchmark for future editions of LEAFF.

***

# Section 1: General Information
`r newthought("This section presents")` a general high-level overview of the film shown and where they were screened.

```{r (HIDE) 1, include = FALSE, echo = FALSE}
# Create text for film titles
txt_film_titles <- data_activity_fund %>% 
  head(5) %>% 
  select(FilmTitle, YearOfRelease) %>% 
  mutate(DummyText_1 = " (", DummyText_2 = ")") %>% 
  select(FilmTitle, DummyText_1, YearOfRelease, DummyText_2) %>% 
  unite(col = Text, FilmTitle, DummyText_1, YearOfRelease, DummyText_2, sep = "") %>% 
  pull()
txt_film_titles <- paste0(txt_film_titles[1:4]) %>% 
  append(txt_film_titles[5])

# Create text for film screenings
txt_film_screenings <- data_activity_fund %>% 
  distinct(VenueName) %>% 
  pull()
txt_film_screenings <- paste0(txt_film_screenings[1:3]) %>% 
  append(txt_film_screenings[8])

# Create text for accessibility
n <- nrow(data_activity_fund)

n_access <- data_activity_fund %>% 
  filter(was_this_an_accessibility_screening == "Yes") %>% 
  nrow()
  
n_subtitles <- data_activity_fund %>% 
  filter(if_this_was_accessible_you_can_show_us_which_type_using_dropdown_the_options == "Captioned / Descriptive Subtitles") %>% 
  nrow()
  
if (n == n_access) {
  txt_access <- "all"
} else if(n/2 < n_access) {
  txt_access <- "most"
} else if (n_access > 0) {
  txt_access <- "some"
} else {
  txt_access <- "none"
}

if (n_access == n_subtitles) {
  txt_subtitles <- "all"
} else if(n_access/2 < n_subtitles) {
  txt_subtitles <- "most"
} else if (n_subtitles > 0) {
  txt_subtitles <- "some"
} else {
  txt_subtitles <- "none"
}

# Create text for events
txt_event <- data_activity_fund %>% 
  filter(!is.na(event_type_where_more_than_just_a_screening_eg_q_a)) %>% 
  distinct(event_type_where_more_than_just_a_screening_eg_q_a) %>% 
  pull()
txt_event <- paste0(txt_event[1:length(txt_event)-1]) %>% 
  append(txt_event[nrow(txt_event)])

```

## Section 1.1: Films Shown and Locations

+ For the 2017 festival a wide range of films from different nations that included South Korea, Japan, Hong Kong, Vietnam, and the Phillippines were shown. ^[[Full programme here](https://www.leaff.org.uk/programme-2/)] These included `r toString(txt_film_titles)`. 

+ The screenings for these films took place in a variety of locations, mostly in London, but with a few in other regions in the UK. These included `r toString(txt_film_screenings)`.

## Section 1.2: Accessibility
+ For each of these film screenings, `r toString(txt_access)` of them were an **accessibility screening**. Of those that were an **accessbility screening**, `r toString(txt_subtitles)` of them had descriptive subtitles and/or were captioned.

## Section 1.3: Additional Events
+ Beyond showing films, LEAFF 2017 offered audiences the chance to be more involved with films and cinema by hosting a series of events to accompany some of the festival's film screenings. These events involved sessions such as `r toString(txt_event)`.

## Section 1: Summary
Given the range of films screened, the way these screenings met accessibility requirements, and the additional events that were hosted during the festival to complement the films, then LEAFF 2017 offered all audiences an eclectic range of activities and films to enjoy.

***

# Section 2: Audience Demographics
`r newthought("This section presents")` data on the demographics of people who have attended LEAFF 2017, and filled in our post-screening surveys.

```{r 1. (HIDE) Remove variables, include = FALSE, echo = FALSE}
rm(txt_access, txt_event, txt_film_screenings, txt_film_titles, txt_subtitles)
```


## Section 2.1: Gender
```{r (HIDE) 2.1 Gender - text, include = FALSE, echo = FALSE}
data_gender <- data_demographics %>% 
  filter(Category == "Gender" & Field != "prefer not to say / did not answer") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2))

value_female <- data_gender %>% 
  filter(Field == "Female") %>% 
  select(Percent) %>% 
  pull()
value_male <- data_gender %>% 
  filter(Field == "Male") %>% 
  select(Percent) %>% 
  pull()

# Create text for gender closeness
if(value_female == value_male) {
  txt_gender <- "equal"
} else if (abs(value_female - value_male) < 0.3) {
  txt_gender <- "similar"
} else {
  txt_gender <- "far apart"
}
```

```{r (SHOW) 2.1 Gender - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 1", fig.width = 5, fig.height = 3}
func_plot_pie(x = data_gender, col_counts = "Percent", col_category = "Field", 
              plot_title = "Gender", factor_levels = c("Male", "Female"))
```
+ In **Figure 1**, the female-to-male proportion of audience who went to the film screenings during the festival and completed this field in the post-film survey  is `r toString(txt_gender)`, `r toString(paste0(value_female * 100, "%"))` to `r toString(paste0(value_male * 100, "%"))`.

## Section 2.2: Age
```{r (HIDE) 2.2 Age - text, include = FALSE, echo = FALSE}
data_age <- data_demographics %>% 
  filter(Category == "Age") %>% 
  arrange(desc(Value))

txt_age <- data_age %>% 
  select(Field) %>% 
  head(3) %>% 
  pull()
```
```{r (SHOW) 2.2 Age - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 2", fig.width = 5, fig.height = 3}
func_plot_counts_percents(x = filter(.data = data_demographics_master, Category == "Age"), col_x = "Field",
                          colour_fill = cb_palette[["cb_orange"]], plot_title = "Age", plot_title_x = "Age")
```
+ In **Figure 2**, the largest three age groups for our audience who went to the film screenings during the festival and completed this field in the post-film survey are the `r toString(txt_age)` categories. 

+ This ties in with the festival's aim to attract and engage young age groups in film and cinema, as it is the young age groups who will be the future consumers of film and cinema.


## Section 2.3: Ethnicity
```{r (HIDE) 2.3 Ethnicity - text, include = FALSE, echo = FALSE}
data_ethnicity <- data_demographics %>% 
  filter(Category == "Ethnicity") %>% 
  arrange(desc(Value)) %>% 
  select(Field, Value)

txt_ethnicity <- data_ethnicity %>% 
  head(3) %>% 
  select(Field) %>% 
  pull()
txt_ethnicity_top_two <- data_ethnicity %>% 
  mutate(OpenBracket = " (", EndBracket = ")") %>%
  select(Field, OpenBracket, Value, EndBracket) %>% 
  head(2) %>% 
  unite(col = Text, Field, OpenBracket, Value, EndBracket, sep = "")
```
```{r (SHOW) 2.3 Ethnicity - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 3", fig.width = 5, fig.height = 3}
func_plot_counts_percents(x = filter(.data = data_demographics_master, Category == "Ethnicity"), col_x = "Field",
                          colour_fill = cb_palette[["cb_light_blue"]], plot_title = "Ethnicity", plot_title_x = "Ethnicity")
```
+ In **Figure 3**, the largest three ethnicity groups for our audience who went to the film screenings during the festival and completed this field in the post-film survey are `r toString(txt_ethnicity)`.

```{marginfigure}
_This would appeal most to sponsors who want to improve their brand exposure to different ethnic groups._
```

+ Notice in particular that the number of *`r toString(txt_ethnicity_top_two[1,])`* and *`r toString(txt_ethnicity_top_two[2,])`* ethnic groups who attended LEAFF 2017 are very close. This demonstrates that the film festival is effective in appealing to both an East Asian and non-East Asian audiences.

## Section 2: Summary
Given the relatively equal split between genders, the popularity of the festival with younger age groups, and the festival's ability to attract both East Asian and non-East Asian ethnic groups, LEAFF 2017 was effective in catering to the key audience group of younger adults equally between genders, and within this subgroup, attracting a wide range of people from different ehtnic backgrounds.

***

# Section 3: Key Performance Metrics
`r newthought("This section presents")` key analyis of the festival's performance data.
```{r 2. (HIDE) Remove variables, include = FALSE, echo = FALSE}
rm(data_gender, data_age, data_ethnicity, txt_gender, value_male, value_female,
   txt_age, txt_ethnicity, txt_ethnicity_top_two)
```

## Section 3.1: Total admissions for each film
```{r (HIDE) 3.1 Admissions - text, echo = FALSE, include = FALSE}
data_admissions <- data_activity_fund %>% 
  filter(!(YearOfRelease %in% c("various", "__"))) %>% 
  select(FilmTitle:YearOfRelease, TotalAdmissions) %>%
  # get proper ordering of most popular films
  group_by(FilmTitle) %>% 
  summarise(TotalAdmissionsOverall = sum(TotalAdmissions)) %>% 
  arrange(desc(TotalAdmissionsOverall)) %>% 
  left_join(y = data_activity_fund, by = "FilmTitle") %>% 
  select(FilmTitle, YearOfRelease, VenueName, TotalAdmissionsOverall, TotalAdmissions) %>% 
  rename(TotalAdmissionsByCinema = TotalAdmissions)

# Create table for printing
table_admissions <- data_admissions %>% 
  distinct(FilmTitle, .keep_all = TRUE) %>% 
  select(-TotalAdmissionsByCinema) %>% 
  rename(Film = FilmTitle,
         `Release Year` = YearOfRelease,
         Venue = VenueName,
         `Total Admissions` = TotalAdmissionsOverall) %>% 
  head(5) 

n_open_gala <- 1679
n_admissions_gala <- table_admissions %>% 
  head(1) %>% 
  select(`Total Admissions`) %>% 
  pull()
value_gala_admissions_proportion <- (n_admissions_gala / n_open_gala) * 100
value_gala_admissions_proportion <- round(x = value_gala_admissions_proportion, digits = 2)
```
```{r (SHOW) 3.1 Admissions - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 4", fig.width = 7, fig.height = 10}
ggplot(data = data_admissions, 
       mapping = aes(x = reorder(x = FilmTitle, X = TotalAdmissionsOverall), y = TotalAdmissionsByCinema)) +
  geom_bar(mapping = aes(fill = factor(VenueName)), stat = "identity") +
  coord_flip() +
  labs(title = "Bar Chart: Total Admissions by Film and Venue", subtitle = "LEAFF 2017", 
       x = "Film", y = "Total Admissions", fill = "Venue") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
                      plot.subtitle = element_text(face = "bold", hjust = 0.5),
                      panel.background = element_blank(),
                      axis.line = element_line(color = cb_palette["cb_black"]))
```
+ In **Figure 4**, we have the number of people who bought tickets for each of the film screenings, with the colour-coding distinguishing which films were shown in which cinemas. In particular, it is worth noting that the most-watched film, *The Fortress*, was held at *Odeon Leicester Square*, which has a screen capacity of *`r toString(n_open_gala)`*; whereas the other cinemas where films were shown have much smaller capacities. 

+ The table below focusses on the key insight of the most popular films that can be drawn from **Figure 4**. Whilst we do not possess data on the seating capacity for each venue, and consequently cannot make a more accurate inference on which films sold the most tickets relative to the number of tickets available, we do know that for opening gala film, *The Fortress*, `r toString(paste0(value_gala_admissions_proportion, "%"))` of available tickets were sold.
```{r (SHOW) 3.1 Admissions - table, echo = FALSE}
kable(table_admissions, caption = "_The most popular films by admissions for LEAFF 2017_")
```

## Section 3.2: Retaining old audiences and capturing new audiences
```{r (HIDE) 3.2 Retention - text, echo = FALSE, include = FALSE}
data_retention <- data_demographics %>% 
  filter(Category == "New   Audience" & Field != "Prefer not to say / did not answer") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2)) %>% 
  arrange(desc(Value))

txt_retention_first <- data_retention %>% 
  head(1)
txt_retention_first <- paste0(select(.data = txt_retention_first, Value),
                              " of LEAFF 2017 attendees saying ", 
                              "\"", select(.data = txt_retention_first, Field), "\"")
txt_retention_second <- data_retention[2, ]
txt_retention_second <- paste0(select(.data = txt_retention_second, Value),
                              " of LEAFF 2017 attendees saying ", 
                              "\"", select(.data = txt_retention_second, Field), "\"")
```
```{r (SHOW) 3.2 Retention - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 5", fig.width = 6, fig.height = 5}
lvls <- c("Been to LEAFF 2015", "Been to LEAFF 2016",
          "Been to both", "This is my first time")
func_plot_pie(x = data_retention, col_counts = "Percent", col_category = "Field", 
              plot_title = "Audience Retention", factor_levels = lvls)
```
+ In **Figure 5**, we have `r toString(txt_retention_first)` and `r toString(txt_retention_second)`. 

+ These were the top two responses and demonstrates that LEAFF 2017's marketing strategy was effective in encouraging attendees from 2016 to return to LEAFF 2017 and in attracting new attendees.

## Section 3.3: Audience rating of their LEAFF 2017 experience
```{r (HIDE) 3.3 Rating- text, echo = FALSE, include = FALSE}
data_rating <- data_demographics %>% 
  filter(Category == "Rating of the experience") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2)) 

txt_rating <- data_rating %>% 
  filter(Field %in% c("Brilliant       *****", "****"))
txt_rating <- sum(x = txt_rating$Percent)

if (txt_rating > 0.7) {
  txt_rating_conc <- c("the majority of", "successful")
} else if (txt_rating > 0.5) {
  txt_rating_con <- c("over half of", "successful")
} else {
  txt_rating_conc <- c("some", "unsuccessful")
}
```
```{r (SHOW) 3.3 Rating - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 6", fig.width = 5, fig.height = 4}
lvls <- c("Brilliant       *****", "****", "***", "**", "Poor *")
data_rating <- data_demographics_master %>% 
  filter(Category == "Rating of the experience") %>% 
  mutate(Field = factor(x = Field, levels = lvls))
func_plot_counts_percents(x = data_rating, 
                          col_x = "Field",
                          colour_fill = cb_palette[["cb_green"]], 
                          plot_title = "Rating of Experience", 
                          plot_title_x = "Rating")
```
+ In **Figure 6**, `r toString(paste0(txt_rating * 100, "%"))` of attendees rated their LEAFF 2017 experience as being either **Brilliant \*\*\*\*\* ** (*five stars*) or **Good \*\*\*\* ** (*four stars*).

+ This demonstrates that `r toString(txt_rating_conc[1])` attendees enjoyed LEAFF 2017 and that the programme and activities which were part of this were `r toString(txt_rating_conc[2])` in capturing the public's interests and appetite for film and cinema.

## Section 3.4: Audience main motivation for attending
```{r (HIDE) 3.4 Motivation - text, echo = FALSE, include = FALSE}
data_motivation <- data_demographics %>% 
  filter(Category == "main motivation to attend?") %>% 
  mutate(Percent = round(x = Value/sum(Value), digits = 2)) 

threshold <- 100

txt_motivation <- data_motivation %>% 
  filter(Value > threshold) %>% 
  select(Field) %>% 
  pull()

txt_motivation_count <- data_motivation %>% 
  distinct(Field) %>% 
  nrow()

if (txt_motivation_count > 6) {
  txt_motivation_range <- "diverse and far-reaching"
} else {
  txt_motivation_range <- "concentrated"
}
```
```{r (SHOW) 3.4 Motivation - plot, echo = FALSE, fig.margin = TRUE, fig.cap = "Figure 7", fig.width = 5, fig.height = 4}
lvls <- data_motivation %>% 
  arrange(desc(Value)) %>% 
  select(Field) %>% 
  pull()
data_motivation <- data_demographics_master %>% 
  filter(Category == "main motivation to attend?") %>% 
  mutate(Field = factor(x = Field, levels = lvls, labels = lvls))
func_plot_counts_percents(x = data_motivation, 
                          col_x = "Field",
                          colour_fill = cb_palette[["cb_yellow"]], 
                          plot_title = "Main Motivation for Attending", 
                          plot_title_x = "Motivation Reason") +
  # add text-wrapping for x labels
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))
```
+ In **Figure 7**, the main reasons most people attended were `r toString(txt_motivation)`. ^[*Main reasons* being defined as those reasons which have received more than `r toString(threshold)` responses in the post-film survey.] 

+ Indeed **Figure 7** complements **Figure 6** by providing the core reasons for why festival attendees gave such a positive response of their LEAFF 2017 experience. 

+ **Figure 7** also demonstrates how `r toString(txt_motivation_range)` the reasons for why people attend the festival are, thereby illustrating that the festival caters for a number of preferences, tastes and interests. In this regard, LEAFF 2017 was able to engage with attendees on many levels.

## Section 3.5: Audience likelihood of attending future LEAFFs
```{r (HIDE) 3.5 Future - text, echo = FALSE, include = FALSE}
table_future <- data_demographics %>% 
  filter(Category == "Likelihood of attending again?") %>% 
  mutate(Percent = Value/sum(Value)) %>% 
  select(-Category)

txt_future <- table_future %>% 
  filter(Field %in% c("Very Likely", "Likely")) %>% 
  mutate(PercentFinal = sum(x = Percent) * 100) %>% 
  distinct(PercentFinal) %>% 
  pull() %>% 
  signif(digits = 2) %>% 
  paste0("%")
```
+ In the table below, `r toString(txt_future)` of respondents said they were either **Likely** or **Very Likely** to attend LEAFF in the future.

```{r (SHOW) 3.5 Future - table, echo = FALSE, fig.margin = TRUE}
table_future <- table_future %>% 
  mutate(Percent = paste0(round(x = Percent, digits = 2) * 100, "%"))
pander(x = table_future, 
       caption = "_Likelihood of audience returning for future LEAFF editions based on their experience of LEAFF 2017_")
```

+ This demonstrates that the festival was effective in encouraging people to watch more East Asian film and cinema.

## Section 3: Summary
+ Given that a high and similar number of `r toString(txt_retention_first)` and `r toString(txt_retention_second)`, `r toString(paste0(txt_rating * 100, "%"))` of attendees rated their LEAFF 2017 experience as being either **Brilliant \*\*\*\*\* ** (*five stars*) or **Good \*\*\*\* ** (*four stars*) then this demonstrates that the festival was left a lasting impression on audiences such that `r toString(txt_future)` of respondents are either **Likely** or **Very Likely** to attend LEAFF in the future.
    
***

# Concluding Remarks
```{r 3. (HIDE) Remove variables, include = FALSE, echo = FALSE}
rm(data_admissions, table_admissions, n_open_gala, n_admissions_gala,value_gala_admissions_proportion, 
   data_retention, txt_retention_first, txt_retention_second, 
   data_rating, txt_rating, txt_rating_conc, 
   data_motivation, threshold, txt_motivation, txt_motivation_range,
   table_future, lvls)
```
+ From the data analysed in this report, the key findings are:

**The curated film programme at LEAFF 2017 catered to a mainstream and large audience, and more particularly, being of most interest to the key age groups of 20 - 30.**

**The marketing strategy attracted a good range of people from different backgrounds who were new to the festival and returned to the festival from previous years.**

**The additional events such as Q&A sessions and workshops successfully engaged audiences enough to develop their interest and intrigue in film beyond just watching film.**

**The overall delivery of the entire festival was effective in receiving positive reviews from attendees.**

**Lastly, the overall festival experience was of such quality that `r toString(txt_future)` of survey respondents will return again in the future.**


```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
